\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-13 manuscript.Rmd

```{r dependencymanager, include = FALSE}
library(packrat)
packrat::init()
packrat::snapshot(ignore.stale=TRUE) #use to find and install required dependencies.
```

>>>>

```{r dependencymanager, include = FALSE}
library(packrat)
packrat::init()
#Only use when you have added some pack
#packrat::snapshot(ignore.stale=TRUE)

#To find and install required dependencies.
packrat::restore()
```
